---
title: "Info and Contacts"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# {.tabset}

## News


```{r, echo=FALSE}
id_info<-"https://docs.google.com/u/0/uc?id=13QMciIIPwQC3GBQZ0asJfnPtJVkcPIGA&export=download"
htmltools::includeHTML(id_info)
```

## Signal an issue

For any issue regarding the Conference, please contact the Welcome desk or write an email to the
<a href = "mailto:sis2022@google.com?subject=Conference issue&body=Dear SIS2022 Organization,%0D%0A I am (name, surname)  %0D%0A I need support for the following issue: %0D%0A">
Local Organizing Committee
</a>

### LOCAL ORGANIZING COMMITTEE

- __Rosanna Verde  (Chair)__– _Università della Campania_
- Antonio Balzanella – _Università della Campania “Luigi Vanvitelli”_
- Ida Camminatiello – _Università della Campania “Luigi Vanvitelli”_
- Lelio Campanile – _Università della Campania “Luigi Vanvitelli”_
- Stefania Capecchi – _Università di Napoli “Federico II”_
- Antonio De Falco – _Università di Napoli “Federico II”_
- Domenico De Stefano - _Università di Trieste_
- Andrea Diana – _Università della Campania “Luigi Vanvitelli”_
- Michele Gallo – _Università di Napoli “L’Orientale”_
- Giuseppe Giordano – _Università di Salerno_
- Ferdinando Grillo – _Università della Campania “Luigi Vanvitelli”_
- Mauro Iacono – _Università della Campania “Luigi Vanvitelli”_
- Antonio Irpino – _Università della Campania “Luigi Vanvitelli”_
- Rosaria Lombardo – _Università della Campania “Luigi Vanvitelli”_
- Michele Mastroianni – _Università della Campania “Luigi Vanvitelli”_
- Fabrizio Maturo – _Università della Campania “Luigi Vanvitelli”_
- Fiammetta Marulli – _Università della Campania “Luigi Vanvitelli”_
- Paolo Mazzocchi – _Università di Napoli “Parthenope”_
- Marco Menale – _Università della Campania “Luigi Vanvitelli”_
- Stefania Nacchia – _Università della Campania “Luigi Vanvitelli”_
- Giuseppe Pandolfi - _Università di Napoli “Federico II”_
- Antonella Rocca – _Università di Napoli “Parthenope”_
- Elvira Romano – _Università della Campania “Luigi Vanvitelli”_
- Biagio Simonetti – _Università del Sannio_


## Where to eat

- [A selection from Tripadvisor](https://www.tripadvisor.it/Restaurants-g194713-Caserta_Province_of_Caserta_Campania.html)
- [Where to eat a good pizza](https://eataliantraveler.com/where-to-eat-the-best-pizza-in-caserta/)

## What to see around

Dear participant, 

do you have some spare time? These links will help you to organizing your stay in Caserta:

- [Suggestions from Tripadvisor](https://www.tripadvisor.it/Attractions-g194713-Activities-Caserta_Province_of_Caserta_Campania.html)
- [Official Website of the ROyal Palace of Caserta (Reggia)](https://reggiadicaserta.cultura.gov.it/)

How to move in or around Caserta

- [Urban public transport](https://aircampania.it/linee-e-orari/linee-caserta/)
- [Extraurban public transport](https://www.atcbus.it/p/autolinee_reg_nuovi_orari.htm)
- [Taxi service](http://www.serviziotaxicaserta.it/)
- [Scooter and sustainable mobility](https://updates.moovit.com/94349-2/)

## Program committee

- __Matilde Bini (Chair)__ - _Università Europea di Roma_
- Giovanna Boccuzzo - _Università degli studi di Padova_
- Antonio Canale - _Università degli studi di Padova_
- Maurizio Carpita - _Università degli studi di Brescia_
- Carlo Cavicchia - _Erasmus University Rotterdam_
- Claudio Conversano - _Università degli studi della Cagliari_
- Fabio Crescenzi - _ISTAT_
- Domenico De Stefano - _Università di Trieste_
- Lara Fontanella - _Università degli studi di Chieti-Pescara_
- Ornella Giambalvo - _Università degli studi di Palermo_
- Gabriella Grassia - _Università degli Studi di Napoli Federico II_
- Tiziana Laureti - _Università della Tuscia_
- Caterina Liberati - _Università degli studi di Milano-Bicocca_
- Lucio Masserini - _Università degli studi di Pisa_
- Cira Perna - _Università degli studi Salerno_
- Pier Francesco Perri - _Università degli studi della Calabria_
- Elena Pirani - _Università degli studi di Firenze_
- Gennaro Punzo - _Università degli studi di Napoli Parthenope_
- Emanuele Raffinetti - _Università degli studi di Pavia_
- Matteo Ruggiero - _Università degli studi di Torino_
- Salvatore Strozza - _Università degli studi di Napoli Federico II_
- Rosanna Verde - _Università della Campania Luigi Vanvitelli, Caserta_
- Donatella Vicari - _Università degli studi La Sapienza, Roma_
